`sdmTMB`: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-07-20 doc/paper.Rmd
add more notes

@@

>>>>

<!-- # For submission to MEE as an Application paper -->

@@

# Tables

1. Comparison to related software?

- VAST
- INLA
- mgcv
- glmmTMB
- glmmfields?
- other stuff on CRAN, spBayes etc.

# Figures

1. Flow diagram of functions? Not needed?
1. Speed with various knots and/or spatial complexity in comparison to INLA + VAST + ...?
1. Example application 1 - SDM, show mesh(?) and/or raw data, show predictions and SD in space,
1. Example application 2 - population index with stitched survey?
